### 2023-10-23 results/celegans.tex
No work was done

@@

\subsection{Analog results}

Let's focus on a single data sequence, for simplicity. The training data sequence found in \cref{graph:io5Celegans}.

@@

The best looking output of the four predicted neurons responses is the one from PVR. That is confirmed by its \ac{RMSE} with the digital prediction. It is the lowest of the four, however, it isn't close enough to the digital prediction.

>>>>

The results will be analyzed by focusing on a single data sequence, the training data sequence available in \cref{graph:io5Celegans}.

@@

\subsection{Analog results}
\label{subsec:analogCelegans}

It's been established in \cref{sec:resAirline}, that the analog circuit with a serial size of one ($n_s=1$) show a lower \ac{RMSE} to the digital predictions than the digital predictions.

Due to the complexity of the dataset, the simulation were only ran using a serial size of one ($n_s=1$) to get the best looking results.

@@

The best looking output of the four predicted neurons responses is the one from PVR. That is confirmed by its error rate to the digital prediction. It is the lowest of the four, however, it isn't close enough to the digital prediction.
